Thomas et al. 2025

### 2025-01-10 AT_2025.qmd
Formatting updates

---
title: "Thomas et al. 2025"
format: 
  html:
    embed-resources: true
standalone: true
---

@@

## Publication information

**Title:** Trifunctional lipid derivatives: PE’s mitochondrial interactome

**Authors:** Alix Thomas, Rainer Mueller, Ana Kojic, Scotland E. Farley, Frank Stein, Per Haberkant, Carsten Schultz*

(* corresponding: <schulcar@ohsu.edu>{target="_blank"})

**Date published:**

**Journal, ISSN:** Chemical Communications, 1359-7345, 1364-548X

**DOI:** <https://doi.org/10.1039/D4CC03599B>{target="_blank"}

@@

{{< downloadthis DataTables/AT_ChemicalCommunications_2025.csv dname="AT_ChemicalCommunications_2025">}}

>>>>

---
title: "Thomas et al. 2025"
subtitle: "Trifunctional lipid derivatives: PE’s mitochondrial interactome"
format: 
  html:
    embed-resources: true
standalone: true
---

@@

Alix Thomas, Rainer Mueller, Ana Kojic, Scotland E. Farley, Frank Stein, Per Haberkant, Carsten Schultz

Correspondence: <schulcar@ohsu.edu>{target="_blank"}

Chemical Communications

<https://doi.org/10.1039/D4CC03599B>{target="_blank"}

@@

{{< downloadthis DataTables/AT_ChemicalCommunications_2025_download.csv dname="AT_ChemicalCommunications_2025">}}
